Testing atlantisom: end to end truth for California Current

### 2019-05-21 Atlantisom2SSworkflowtest.Rmd
add CC climate 1 testing

---
title: "Testing atlantisom: true biomass output from Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

## Simulate a survey part 1: census to compare with truth

@@

@@

@@

@@

@@

@@

```{r ss-biolsampling}

@@

@@

@@

@@

```{r testcatchbio}

@@

>>>>

---
title: "Testing atlantisom: end to end truth for California Current"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

## Test survey functions: census to compare with truth

@@

surv_cv <- data.frame(species=survspp, cv=rep(0.0,length(survspp)))

@@

### True biomass survey I

@@

### True numbers survey

@@

### Biological sampling: true numbers at age class

@@

### Biological sampling: setup

@@

```{r ss-biolsampling, warning=FALSE, message=FALSE}

@@

### Biological sampling: true lengths and weight-at-age

@@

### True biomass survey II

@@

## Test fishery functions: compare census with truth

@@

```{r testcatchbio1}

#just try the three species for now
catchbio_census_ss <- create_fishery_subset(dat = truth$catchbio,
                                         time = timeall,
                                         species = spp.name,
                                         boxes = boxall)

catchbio_census_ss_agg <- aggregate(atoutput ~ species + time,
                                    data=catchbio_census_ss, sum)

# learned the hard way this can be different from ecosystem outputs
fstepperyr <- if(runpar$outputstepunit=="days") 365/runpar$toutfinc

# what does the output look like?
catchB_outstep <- ggplot() +
  geom_line(data=catchbio_census_ss_agg, aes(x=time/fstepperyr,y=atoutput, color="catch atlantisom"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

catchB_outstep + 
  facet_wrap(~species, scales="free")

@@

It doesnt. A hack gets it closer, suggesting that the problem is a bug in the output for models using codebases prior to late 2015 (CCA is mid-2015).

```{r testcatchbio2}

# should it be aggregated? I just did this above
catchbio_series <- sample_survey_numbers(catchbio_census_ss, surv_cv)

# if it is the pre-2015 bug mentioned in atlantis wiki, this may get it close
catchbio_series_adjust <- catchbio_series %>%
  mutate(atoutput = atoutput/(86400*4))

#does it match catch.txt (which should be in tons)?
atCtxt <- read.table(file.path(d.name, catch.file), header=T)
atCtxt <- atCtxt[, -grep("TsAct", colnames(atCtxt))] #hardcoded for catch.txt output

fishedlookup <- funct.groups %>%
  filter(IsFished > 0)

atCtxttidy <- atCtxt %>%
  rename_(.dots=with(fishedlookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, catchbio, -Time) %>%
  filter(species %in% levels(catchbio_series$species))

compare_catchB <-ggplot() +
  geom_line(data=catchbio_series_adjust, aes(x=time,y=atoutput, color="catch atlantisom"), 
            alpha = 10/10) +
  geom_point(data=atCtxttidy, aes(x=Time/365,y=catchbio, color="txt output catch bio"),
             alpha = 1/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

compare_catchB + 
  facet_wrap(~species, scales="free")

Test this with NOBA model, which may be in the codebase that doesn't have this problem with the CATCH.nc file.
